### 2025-04-11 submissions/02-irap/manuscript_main.tex
submit to IRAE

I measure Asian identity using the Current Population Survey (CPS), which allows me to construct an objective measure of the Asian identity of minors living with their parents. I will use the information on the place of birth, parent's place of birth, and place of birth of grandparents to construct an objective Asian measure.\footnote{Following the works of \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}.} Thus, I could perfectly identify and construct a dataset of first-, second-, and third-generation Asian immigrants (see Figure \ref{fig:diag} for a visual representation). This will consequently allow me to build an objective measure of the Asian identity of minors under the age 17 living with their parents.

@@

To construct a measure of prejudice, I use the implicit association test, the American National Election Studies, and hate crimes against Asians. The implicit association test measures how people associate concepts---for example, Black and dark-skinned people---and evaluations---good, bad. Respondents are asked to quickly match words into categories shown on a screen. Figure (\ref{fig:iatexamples}) shows a few examples of what a test taker would see on a skin tone implicit association test by Harvard's Project Implicit.

@@

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in bias is associated with a 8 percentage points decrease in self-reported Asian identity.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 72 percentage points when the mother is the proxy, 72 percentage points when the father is the proxy, and 87 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

>>>>

I measure Asian identity using the Current Population Survey (CPS) from the 2004-2021, which allows me to construct an objective measure of the Asian identity of minors living with their parents. I will use the information on the place of birth, parent's place of birth, and place of birth of grandparents to construct an objective Asian measure.\footnote{Following the works of \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}.} Thus, I could perfectly identify and construct a dataset of first-, second-, and third-generation Asian immigrants (see Figure \ref{fig:diag} for a visual representation). This will consequently allow me to build an objective measure of the Asian identity of minors under the age 17 living with their parents.

@@

To construct a measure of prejudice, I use the implicit association test, the American National Election Studies, and hate crimes against Asians from the 2004-2021. The implicit association test measures how people associate concepts---for example, Black and dark-skinned people---and evaluations---good, bad. Respondents are asked to quickly match words into categories shown on a screen. Figure (\ref{fig:iatexamples}) shows a few examples of what a test taker would see on a skin tone implicit association test by Harvard's Project Implicit.

@@

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for all generations in panel (A) and for sub-samples of first-, second-, and third-generations in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in bias is associated with a 8 percentage points decrease in self-reported Asian identity.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Hispanic identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 72 percentage points when the mother is the proxy, 72 percentage points when the father is the proxy, and 87 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

### 2025-04-11 submissions/02-irap/manuscript_title_etc.tex
submit to IRAE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of implicit ethnic bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points for all immigrants. A one standard deviation increase in bias decreases self-reported Asian identity by 8 and 9 percentage points for second- and third-generation Asians respectively. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
    \PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points for all immigrants. A one standard deviation increase in bias decreases self-reported Asian identity by 8 and 9 percentage points for second- and third-generation Asians respectively. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
    \PAPERJEL}

### 2025-04-11 submissions/02-irap/tab45-iat_regression_tab_bygrandparent_type.tex
submit to IRAE

\begin{table}[H]

\caption{Relationship Between Bias and Self-Reported Asian identity Among Third-Generation Asian Immigrants: By Grandparental Type \label{regtab-bygrandparents}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Number of Asian Grandparents} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{(1) \\ One} & \specialcell{(2) \\ Two} & \specialcell{(3) \\ Three} & \specialcell{(4) \\ Four}\\
\midrule
Bias & -0.24* & -0.60*** & -2.34*** & -0.24\\
 & (0.14) & (0.17) & (0.78) & (0.20)\\
Female & 0.00 & 0.00 & 0.01 & -0.02*\\
 & (0.01) & (0.02) & (0.03) & (0.01)\\
College Graduate: Mother & 0.01 & 0.04** & 0.11 & -0.02\\
 & (0.01) & (0.02) & (0.09) & (0.02)\\
College Graduate: Father & -0.03*** & 0.00 & -0.03 & 0.02**\\
 & (0.01) & (0.03) & (0.06) & (0.01)\\
\midrule
Observations & 30,052 & 26,255 & 1,324 & 11,751\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) restricted to third-generation Asian immigrants by 
                      number of Asian grandparents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include third-generation Asian children ages 17 and below who live in intact families. 
                      Native-born third-generation Asian 
                      immigrant children with at least one grandparent born in a Asian 
                      country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Self-Reported Asian identity Among Third-Generation Asian Immigrants: By Grandparental Type \label{regtab-bygrandparents}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Number of Asian Grandparents} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{(1) \\ One} & \specialcell{(2) \\ Two} & \specialcell{(3) \\ Three} & \specialcell{(4) \\ Four}\\
\midrule
Bias & -0.01 & -0.09 & -0.69** & -0.11\\
 & (0.04) & (0.08) & (0.32) & (0.06)\\
Female & -0.01 & -0.01 & -0.04 & -0.03**\\
 & (0.01) & (0.02) & (0.06) & (0.01)\\
College Graduate: Mother & 0.01 & 0.07** & 0.08 & 0.00\\
 & (0.01) & (0.03) & (0.09) & (0.03)\\
College Graduate: Father & -0.04*** & 0.00 & -0.07 & 0.00\\
 & (0.01) & (0.04) & (0.08) & (0.01)\\
\midrule
Observations & 14,453 & 12,678 & 567 & 5,744\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equation (\ref{eq:identity_reg_bias}) restricted to third-generation Asian immigrants by 
                      number of Asian grandparents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include third-generation Asian children ages 17 and below who live in intact families. 
                      Native-born third-generation Asian 
                      immigrant children with at least one grandparent born in a Asian 
                      country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
